---
title: "Palmer Penguins"
author: "Kenny"
date: "2024-09-14"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

Analyzing a dataset called Palmer Penguins. The palmerpenguins data contains size measurements for three penguin species observed on three islands in the Palmer Archipelago, Antarctica.

```{r}

library(palmerpenguins)
library(skimr)
library(skimr)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(skimr)
library(tidyverse)

```

Get a summary of the data (1)

```{r}
skim_without_charts(penguins)
```

Get a summary of the data (2)

```{r}
colnames(penguins)
```

Get a summary of the data (3)

```{r}
glimpse(penguins)
```

Counting the number of species shows us there are 3 in total as shown from the skim function above

```{r}
penguins %>%
  count(species)
```


Leads dive into some calculation

Mean bill length my sex. Male penguins have longer and deeper bills, longer flippers, and weight more on average.

```{r}
penguins %>%
  group_by(sex) %>%
  summarise(mean(bill_length_mm), mean(bill_depth_mm), mean(flipper_length_mm),mean(body_mass_g))
```


The Island of Biscoe has the penguins wit the most mass

```{r}
penguins %>%
  drop_na() %>%
  group_by(island) %>%
  summarise(mean(body_mass_g))
```


Lets test the correlation between bill length and bill depth. Appears to be weak and negative.

```{r}
bl <- as.numeric(penguins$bill_length_mm)
bd <- as.numeric(penguins$bill_depth_mm)

cor.test(bl,bd)
```



Lets plot some data

```{r}

ggplot(data = penguins) +
  geom_bar(mapping = aes(x = sex))

ggplot(data = penguins) +
  geom_bar(mapping = aes(x = sex, fill = species))

ggplot(data = penguins) +
  geom_point(mapping = aes(x = body_mass_g, y = bill_length_mm ))

ggplot(data = penguins) +
  geom_point(mapping = aes(x = body_mass_g, y = bill_length_mm, color = island ))+
  facet_wrap(~island) +
  labs(title = "Penguin Mass and Bill Length Relationship", subtitle = "By Island") 

ggplot(data = penguins) +
  geom_point(mapping = aes(x = body_mass_g, y = bill_length_mm, color = island ))+
  facet_wrap(~island) +
  labs(title = "Penguin Mass and Bill Length Relationship", subtitle = "By Island")

ggplot(data = penguins) +
  geom_point(mapping = aes(x = body_mass_g, y = bill_length_mm, color = island ))+
  facet_wrap(~island) +
  labs(title = "Penguin Mass and Bill Length Relationship", subtitle = "By Island", x = "body mass in grams", y = "bill length in mm")  

  
```




# Thanks for analyzing with me.




